---
title: "Black Female Economics"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

```{r}
# 1. Load the library we need for plotting
library(ggplot2)
```

```{r}
# 2 Manually enter the data you would like to analyze
comparison_data <- data.frame(
  Year = rep(c(2012, 2014, 2016, 2018, 2020, 2022, 2023, 2024, 2025), each = 2),
  Region = rep(c("National", "Alabama"), times = 9),
  Income = c(
    34089, 23011, # 2012
    35439, 24430, # 2014
    37365, 25980, # 2016
    40251, 27500, # 2018
    43256, 28410, # 2020
    46532, 31238, # 2022
    50470, 31125, # 2023
    57520, 33200, # 2024 
    59800, 34500  # 2025 (Est)
  )
)
```

```{r}
# Create your plot
ggplot(comparison_data, aes(x = factor(Year), y = Income, fill = Region)) +
  geom_col() + 
  facet_wrap(~Region) + 
  theme_minimal() +
  scale_fill_manual(values = c("Alabama" = "red", "National" = "blue")) +
  labs(
    title = "Income Black Women from Obama and Beyond",
    subtitle = "Median Annual Income for Black Women (National vs. Alabama)",
    x = "Year",
    y = "Annual Income ($)",
    caption = "Source: US Census Bureau (2025 values are BLS/Census preliminary estimates)"
  )
```


Goal: My goal was to investigate if Black women in Alabama face a different economic reality compared to the national average. I wanted to specifically see how Black women's income changed from Obama's last term to present day. Many contributing factors can affect the change, but I think looking at the different presidencies is interesting. I chose to do a comparison using Alabama because it is one of the deep Southern states and the majority of Black people in the U.S. reside in the South, so I wanted to see how one state would compare to the national average. 

Product: A faceted bar chart comparing national median earnings for Black women against those specifically in Alabama.

Data: I used a combination of Census Table P-38 (National) and ACS state-level data (Alabama). I filtered for Black women working full-time, year-round.

Interpretation: There is a major disparity of income nationally vs. regionally. While National median income for Black women grew from $34k to $46k, Alabama’s median only reached $31k in the same time frame. The current Alabama salary for Black women is STILL lower than the National salary average 14 years ago. This confirms that geographic location in the South plays a massive role in economic inequality.









`
