---
title: "Hand-Plotted: Cover Song History Visualiztion"
---

> The projects should be numbered consecutively (i.e., in the order in which you began them), and should include for each project a description of the goal, the product (computer program, hand graph, computer graph, etc.), the data, and some interpretation. Reports must be reproducible and of high quality in terms of writing, grammar, presentation, etc.

```{r}
library(ggplot2)
```


```{r}
# 1. Create the data frame with your coordinates
music_note <- data.frame(
  years = c(1950, 1955, 1960, 1955, 1955, 1955, 1955, 1955, 1955, 1955, 1955, 1955, 1962, 1963, 1964, 1965, 1966, 1967, 1968, 1969, 1970, 1971, 1972, 1973, 1980, 1980, 1980, 1980, 1980, 1980, 1980, 1980, 1980, 1985, 1980, 1975, 1956, 1957, 1958, 1959, 1960, 1961, 1974, 1975, 1976, 1977, 1978, 1979),
  black_music_matters = c(2,1, 2, 3, 4, 5, 6, 7, 8, 9, 10, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11,11, 10, 9, 8, 7, 6, 5, 4, 3, 2, 1, 2, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11, 11)
)
```


```{r}
# 2. Plot it with desired color and labs
ggplot(music_note, aes(x = years, y = black_music_matters)) +
  geom_point(size = 3, color = "brown") + 
  lims(x = c(1950, 1985), y = c(0,15)) + 
  theme_minimal() +
  labs(title = "Hand-Plotted: Cover Song History Visualiztion",
       subtitle = "African American Erasure in the Music Industry", x = "Year", y = "Musical Pitch Intensity", caption = "The beam spans 1955-1975, the peak of exploitative cover practices.")
```



### Goal: The goal of this project was to visualize a historical injustice through a symbolic hand-plot. I chose to represent the era between 1950 and 1985, a period where Black artists frequently had their songs "covered" by white artists, often leading to the original song low on the charts, while the covered version would gain fame and recognition. This piece is a tribute to those artists and a reminder of the cultural theft that occurred .

### Product: I created a hand-plotted scatter plot of a beamed eighth note. The two note heads (the circles) represent the foundation of the music, while the high beam connects the years 1955 to 1975. This specific shape was chosen because that twenty-year window represents the peak of the "cover song" era in the music industry.

### Data: This is a coordinate-mapped plot. I mapped the x-axis to a timeline (1950–1985) and the y-axis to a vertical coordinate system to "draw" the structure of the eighth note.

### Interpretation: What I discovered during this process was that the "shape" of history can be told through simple coordinates. By placing the beam specifically between 1955 and 1975, the data points create a visual "ceiling" that represents the period of highest exploitation. By adding the 1950 and 1985 boundaries, the note sits in its proper historical context. 
