---
title: "Cowboy Carter Viz"
---

```{r}
# 1. Load the library we need for plotting
library(ggplot2)
```

```{r}
# Insert Cowboy Carter Lyric Data

songs <- c("Ameriican Requiem", "Blackbird", "16 Carriages", "Texas Hold 'Em", 
           "Spaghettii", "Alligator Tears", "Ya Ya", "II Hands II Heaven", 
           "Tyrant", "Sweet Honey Buckin")

lyrics <- c(472, 169, 448, 534, 366, 227, 562, 621, 638, 740)

initials <- c("AR", "B", "16C", "TH", "S", "AT", "Y", "HH", "T", "SHB")

# Create your data frame
df <- data.frame(songs, lyrics)

#Create Plot
ggplot(df, aes(x = reorder(songs, lyrics), y = lyrics)) +
  geom_bar(stat = "identity", fill = "#8B0000", color = "black", width = 0.7) + 
  coord_flip() + 
  theme_minimal() +
  labs(
    title = "Lyrical Density: Cowboy Carter",
    subtitle = "Analysis of word counts across key tracks",
    x = "",
    y = "Number of Lyrics"
  )

```

# Goal: The goal of this project was to visualize the creative magnitude and density of Beyoncé’s Cowboy Carter. By mapping the lyrical density of key tracks, I wanted to showcase how this album reclaimed the Country genre not just through sound but through an intentional, dense narrative of Black history and resilience.

# Product: I created a Horizontal Bar Plot. Unlike a vertical chart, the horizontal orientation allows for a more readable, list-like comparison of tracks, mirroring the tracklist of a vinyl record. I used a deep maroon and black aesthetic to pay homage to the rodeo and outlaw themes of the album while maintaining a clean, analytical look.

# Data: I mapped the x-axis to the specific Number of Lyrics (ranging from 169 to 740 words) and the y-axis to the Track Titles. I used an ordering transformation to sort the tracks from the most acoustic to the most lyrically dense, allowing for a clear visual crescendo.

# Interpretation: What I discovered during this process was that the album follows a distinct creative expansion. By starting with the intimate foundations of Blackbird (169 words), the data shows a steady climb toward the high-energy, multi-layered storytelling of Sweet Honey Buckiin (740 words). This visualization reveals that the album's complexity isn't random; it is a calculated build-up that honors the depth of Black songwriting.



